Parallel air palletization and tour planning for simultaneous pickup and delivery

### 2023-02-07 latex/comp_or.tex
Test everything again. Still volume unfeasibilities.
Shim still weak

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                       &                           &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{\bf Surplus}           & {$method$}                &{\bf Results}       &{\bf 1}&{\bf 2}&{\bf 3}&{\bf 4}&{\bf 5}&{\bf 6}&{\bf Speed-up} \\
\toprule

\multirow{6}{*}{$1.2$} &\multirow{2}{*}{ Gurobi}& $f$                & 9.75       &  6.34    &  7.61  &   7.43    &       &       &   \\%
&                                               & {\bf run-time (s)} &  8         &   17     &  30    &  114     &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                      & $f$                & 7.00       &  4.20    &  4.12  &  3.54     &       &       &   \\%
&                                               & {\bf run-time (s)} &  < 1       &   3      &    5   &   19    &       &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                    & $f$                & {\bf 9.85} &  7.52    &  8.33  &  7.82     &       &       &   \\%
&                                               & {\bf run-time (s)} &  < 1       &  < 1     &    2   &  8     &       &       &   \\%

@@

$Gurobi^*$ was run with a time limit of 60s per node. The remaining methods were run with a time limit of 1.6s per node, the worst time {\it Shims} took to solve a node.

>>>>

\begin{table}[H]
\centering
\caption{Volume surpluses, methods and scenarios results}  \label{tab:results}
\footnotesize
%\scriptsize
\begin{tabular}{crcccccccc}
\toprule
&                       &                       &\multicolumn{6}{c}{\bf Scenarios}              &{\bf Normalized}\\
\cmidrule{4-9}		
{\bf Surplus}           & {$method$}            &{\bf Results}       &{\bf 1}      &{\bf 2}    &{\bf 3}      &{\bf 4}     &{\bf 5}    &{\bf 6}&{\bf Speed-up} \\
\toprule

\multirow{6}{*}{$1.2$} &\multirow{2}{*}{ Gurobi}& $f$                & {\bf 12.00} & {\bf 8.28} & {\bf 12.19} &  13.38     &       &       &   \\%
&                                               & {\bf run-time (s)} &  8          &   19       &  35         &  133     &    315   &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $Shims$}                      & $f$                & 8.02        &  6.00      &  6.00       &  5.57      &       &       &   \\%
&                                               & {\bf run-time (s)} &  < 1        &   2        &    3        &   12       &   38    &       &   \\%

\cmidrule{2-10}		                       
&\multirow{2}{*}{ $mpShims$}                    & $f$                & 8.58        &  6.87      &  10.90      & 12.99 &  {\bf }     &       &   \\%
&                                               & {\bf run-time (s)} &  < 1        &   2        &    3        &  9        &    27   &       &   \\%

@@

All methods were run with a time limit of 1.8s per node, the worst time {\it Shims} took to solve a node, considering all scenarios and instances.
